### 2021-06-05 paper.tex
Minor typos

It is well known that viscosity in magnetised plasmas (such as that which makes up the solar corona) is anisotropic and strongly dependent on the strength and direction of the local magnetic field~\cite{hollwegViscosityChewGoldbergerLowEquations1986a,hollwegViscosityMagnetizedPlasma1985,Braginskii1965}. The development of the switching model~\cite{mactaggartBraginskiiMagnetohydrodynamicsArbitrary2017} and implementation in Lare3d has allowed the investigation of the effect of anisotropic viscosity on solar phenomena. We find the stability of Lare3d without (the more commonly employed) isotropic or shock viscosity to be sufficient for at least the study of kink instabilities in coronal loops~\cite{quinnEffectAnisotropicViscosity2020a}. The interest in anisotropic viscosity stems from the unanswered question of which heating mechanism (viscous or Ohmic) is dominant in the solar corona~\cite{klimchukSolvingCoronalHeating2006a}, an important facet of solving the coronal heating problem. Using scaling laws, it has been suggested that viscous heating (generated through anisotropic viscosity) can dwarf that of Ohmic heating~\cite{craigAnisotropicViscousDissipation2009a,litvinenkoViscousEnergyDissipation2005}. However, due to computational and observational limitations, this cannot be directly tested, and so the influence of other factors such as small scale instabilities and turbulence is relatively unknown~\cite{klimchukSolvingCoronalHeating2006a}. In addition to directly heating the plasma, viscosity plays a part in the damping of instabilities and waves~\cite{rudermanSlowSurfaceWave2000a}. It is this effect we are most interested in here, and it shall be found that the use of anisotropic viscosity permits the growth of the fluting instability, which is otherwise strongly damped by isotropic viscosity.

@@

The isotropic (or Newtonian) viscosity stress tensor is given by
\begin{equation}
  \label{eq:isotropic_viscous_tensor}
  \ten{\sigma} = \nu \ten{W},
\end{equation}
where $\nu$ is the viscous transport parameter, generally referred to as the viscosity,
\begin{equation}
  \label{eq:rate_of_strain}
  \ten{W} = \nabla\vec{u} + (\nabla\vec{u})^T - \tfrac{2}{3}(\nabla \cdot \vec{u})\ten{I},
\end{equation}
is the rate of strain tensor, and $\ten{I}$ is the  $3\times 3$ identity matrix. We use an identical model of anisotropic viscosity as that used in previous work~\cite{quinnEffectAnisotropicViscosity2020a}, the switching model, first presented in~\cite{mactaggartBraginskiiMagnetohydrodynamicsArbitrary2017}. While this model is intended to revert to an isotropic model in the vicinity of magnetic null points, we effectively only make use of the anisotropic component, since there are no null points present in the simulations at any point. To this end, we set the switching parameter (which controls the degree of viscous anisotropy) to $a_0 = 150$ in Lare3d's control, a value sufficiently large that the anisotropic viscous stress tensor is given by
\begin{equation}
  \label{eq:switching_model}
\ten{\sigma}_{\text{swi}} = \nu \left[\frac{3}{2}(\ten{W}\vec{b}\cdot\vec{b}) \left( \vec{b} \otimes \vec{b} - \frac{1}{3}\ten{I} \right)\right],
\end{equation}
where $\vec{b}$ is the unit vector in the direction of the magnetic field. This tensor is identical to the strong field approximation of Braginskii~\cite{braginskiiTransportProcessesPlasma1965}. Full use of the switching model can be found in~\cite{mactaggartBraginskiiMagnetohydrodynamicsArbitrary2017,quinnEffectAnisotropicViscosity2020a}\todo{ref KHI paper}.

>>>>

It is well known that viscosity in magnetised plasmas (such as that which makes up the solar corona) is anisotropic and strongly dependent on the strength and direction of the local magnetic field~\cite{hollwegViscosityChewGoldbergerLowEquations1986a,hollwegViscosityMagnetizedPlasma1985,braginskiiTransportProcessesPlasma1965}. The development of the switching model~\cite{mactaggartBraginskiiMagnetohydrodynamicsArbitrary2017} and implementation in Lare3d has allowed the investigation of the effect of anisotropic viscosity on solar phenomena. We find the stability of Lare3d without (the more commonly employed) isotropic or shock viscosity to be sufficient for at least the study of kink instabilities in coronal loops~\cite{quinnEffectAnisotropicViscosity2020a}. The interest in anisotropic viscosity stems from the unanswered question of which heating mechanism (viscous or Ohmic) is dominant in the solar corona~\cite{klimchukSolvingCoronalHeating2006a}, an important facet of solving the coronal heating problem. Using scaling laws, it has been suggested that viscous heating (generated through anisotropic viscosity) can dwarf that of Ohmic heating~\cite{craigAnisotropicViscousDissipation2009a,litvinenkoViscousEnergyDissipation2005}. However, due to computational and observational limitations, this cannot be directly tested, and so the influence of other factors such as small scale instabilities and turbulence is relatively unknown~\cite{klimchukSolvingCoronalHeating2006a}. In addition to directly heating the plasma, viscosity plays a part in the damping of instabilities and waves~\cite{rudermanSlowSurfaceWave2000a}. It is this effect we are most interested in here, and it shall be found that the use of anisotropic viscosity permits the growth of the fluting instability, which is otherwise strongly damped by isotropic viscosity.

@@

The isotropic (or Newtonian) viscosity stress tensor is given by
\begin{equation}
  \label{eq:isotropic_viscous_tensor}
  \ten{\sigma}_{iso} = \nu \ten{W},
\end{equation}
where $\nu$ is the viscous transport parameter, generally referred to as the viscosity,
\begin{equation}
  \label{eq:rate_of_strain}
  \ten{W} = \nabla\vec{u} + (\nabla\vec{u})^T - \tfrac{2}{3}(\nabla \cdot \vec{u})\ten{I},
\end{equation}
is the rate of strain tensor, and $\ten{I}$ is the  $3\times 3$ identity matrix. We use an identical model of anisotropic viscosity as that used in previous work~\cite{quinnEffectAnisotropicViscosity2020a}, the switching model, first presented in~\cite{mactaggartBraginskiiMagnetohydrodynamicsArbitrary2017}. While this model is intended to revert to an isotropic model in the vicinity of magnetic null points, we effectively only make use of the anisotropic component, since there are no null points present in the simulations at any point. To this end, we set the switching parameter (which controls the degree of viscous anisotropy) to $a_0 = 150$ in Lare3d's control, a value sufficiently large that the anisotropic viscous stress tensor is given by
\begin{equation}
  \label{eq:switching_model}
\ten{\sigma}_{\text{swi}} = \nu \left[\frac{3}{2}(\ten{W}\vec{b}\cdot\vec{b}) \left( \vec{b} \otimes \vec{b} - \frac{1}{3}\ten{I} \right)\right],
\end{equation}
where $\vec{b}$ is the unit vector in the direction of the magnetic field. This tensor is identical to the strong field approximation of Braginskii~\cite{braginskiiTransportProcessesPlasma1965}. Full use of the switching model can be found in~\cite{mactaggartBraginskiiMagnetohydrodynamicsArbitrary2017,quinnEffectAnisotropicViscosity2020a}\todo{ref KHI paper}.
